func-descr.template

### 2025-11-27 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report, Appendix A: UMGE Model & MF Support Functions description prototype added.

As mentioned in [Chapter 23: *Regularization*, Section 23.7: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the *Course Textbook* the `Movielens` dataset also has a genres column. This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].

@@

Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) mentioned above[@MRS-R-BEST]:
```{r }
# For better visibility, we reduce the data for plotting 
# while keeping the worst and best rating rows:
plot_ind <- odd(1:nrow(genre_ratins_grp))
plot_dat <- genre_ratins_grp_sorted[plot_ind,]

plot_dat |>
  ggplot(aes(x = rating_avg, y = genres)) +
  ggtitle("Genre Average Rating") +
  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
  xlab("Average ratings") +
  ylab("Genres") +
  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
  theme_economist() +
  theme(plot.title = element_text(vjust = 3.5),
        axis.title.x = element_text(vjust = -5, face = "bold"),
        axis.title.y = element_text(vjust = 10, face = "bold"),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

@@

To account for a _genre effect_ we will use the model suggested in the [Chapter 23: *Regularization*, Section 23.7: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the *Course Textbook*:

If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect[@IDS2_23-7]:

>>>>

As mentioned in [Chapter 24: *Regularization*, Section 24.4: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) (*Exercises 9-15*) of the *Course Textbook* the `Movielens` dataset also has a genres column. This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_24-4].

@@

@@

If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:

### 2025-11-27 reports/capstone-movielens.site/05.appendix.Rmd
Report section [UME Model Regularization: Fine-tuning\: review.
Report, Appendix A: UMGE Model & MF Support Functions description prototype added.

### OMR Model Helper Functions
\

@@

### UME Model Utility Functions
\

@@

### UME Model Regularization
\

@@

>>>>

### OMR Model: Helper Functions
\

@@

### UME Model: Utility Functions
\

@@

### UME Model: Regularization
\

@@

### UMGE Model: Utility Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) script on _GitHub_.
:::

#### [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) Function {#func.train_user_movie_genre_effect}
\

Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_genre_effect.args.train_set) argument.

::: { #func.train_user_movie_genre_effect.usage .sidebar }
##### Usage
\

::: { #func.train_user_movie_genre_effect.args .sidebar }
##### Arguments
\

::: { #func.train_user_movie_genre_effect.args.train_set .sidebar }
  - **train_set:** Training dataset;

:::
::: { #func.train_user_movie_genre_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.train_user_movie_genre_effect.details .sidebar }
##### Details
\

The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero). The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::

::: { #func.train_user_movie_genre_effect.value .sidebar }
##### Value
\

Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UM Effect Model*.
:::

::: { #func.train_user_movie_genre_effect.code .sidebar }
##### Source Code
\

The source code of the [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is shown below:
```{r eval=FALSE}
train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_user_movie_genre_effect
`lambda` is `NA`")
  }

  genre_bias <- train.sgr |>
      left_join(edx.user_effect, by = "userId") |>
      left_join(rglr.UM_effect, by = "movieId") |>
      mutate(resid = rating - (mu + a + b)) |>
      group_by(genres) |>
      summarise(g = mean_reg(resid, lambda), n = n())

    train.sgr |>
      left_join(genre_bias, by = "genres") |>
      left_join(rglr.UM_effect, by = "movieId") |>
      group_by(movieId) |>
      summarise(g = mean(g))
}
```

::: {.noteblock data-latex=""}
The source code of the [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) script on _GitHub_.
:::
:::

#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) Function {#func.train_user_movie_genre_effect.cv}
\

::: { #func.train_user_movie_genre_effect.cv.usage .sidebar }
##### Usage
\

::: { #func.train_user_movie_genre_effect.cv.args .sidebar }
##### Arguments
\

::: { #func.train_user_movie_genre_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

::: { #func.train_user_movie_genre_effect.cv.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
:::
:::

::: { #func.train_user_movie_genre_effect.cv.value .sidebar }
##### Value
\

Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
:::

::: { #func.train_user_movie_genre_effect.cv.code .sidebar }
##### Source Code
\

The most important part of the source code of the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is shown below:
```{r eval=FALSE}
train_user_movie_genre_effect.cv <- function(lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_user_movie_genre_effect.cv
`lambda` is `NA`")
  }

  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
Computing User+Movie+Genre Effect...")
  else put_log1("Function `train_user_movie_genre_effect.cv`:
Computing User+Movie+Genre Effect for lambda: %1...",
                lambda)

  put_log1("Function `train_user_movie_genre_effect.cv`:
Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples...", 
           CVFolds_N)

  start <- put_start_date()
  user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
    cv_fold_dat <- edx_CV[[fold_i]]

    put_log2("Processing User+Movie+Genre Effects for %1-Fold Cross Validation samples (Fold %2)...",
             CVFolds_N,
             fold_i)
    umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)

    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
of the %2-Fold Cross Validation samples.",
             fold_i,
             CVFolds_N)
    umg_effect
  })
  put_end_date(start)
  put_log1("Function `train_user_movie_genre_effect.cv`:
User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
           CVFolds_N)

  user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)

  user_movie_genre_effect <- user_movie_genre_effects_united |>
    group_by(movieId) |>
    summarise(g = mean(g))

  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
Training completed: User+Movie+Genre Effects model.")
  else put_log1("Function `train_user_movie_genre_effect.cv`:
Training completed: User+Movie+Genre Effects model for lambda: %1...",
                lambda)

  user_movie_genre_effect
}
```

::: {.noteblock data-latex=""}
The complete source code of the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) script on _GitHub_.
:::
:::

#### [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) Function {#func.calc_user_movie_genre_effect_MSE}
\

::: { #func.calc_user_movie_genre_effect_MSE.usage .sidebar }
##### Usage
\

::: { #func.calc_user_movie_genre_effect_MSE.args .sidebar }
##### Arguments
\

::: { #func.calc_user_movie_genre_effect_MSE.args.test_set .sidebar }
  - **test_set:** Validation dataset;

:::
::: { #func.calc_user_movie_genre_effect_MSE.args.um_effect .sidebar }
  - **um_effect:** Data frame representing the *UM Effect Model*.

::: { #func.calc_user_movie_genre_effect_MSE.details .sidebar }
##### Details
\

The function calculates *Mean Squared Error (MSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.

::: { #func.calc_user_movie_genre_effect_MSE.value .sidebar }
##### Value
\

::: { #func.calc_user_movie_genre_effect_MSE.code .sidebar }
##### Source Code
\

The source code of the [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is shown below:
```{r eval=FALSE}
calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
  test_set |>
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(umg_effect, by = "movieId") |>
    mutate(resid = rating - clamp(mu + a + b + g)) |> 
    pull(resid) |> mse()
}
```

::: {.noteblock data-latex=""}
The source code of the [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) script on _GitHub_.
:::
:::

#### [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) Function {#func.calc_user_movie_genre_effect_MSE.cv}
\

::: { #func.calc_user_movie_genre_effect_MSE.cv.usage .sidebar }
##### Usage
\

::: { #func.calc_user_movie_genre_effect_MSE.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_user_movie_genre_effect_MSE.cv.args.um_effect .sidebar }
  - **um_effect:** Data frame representing the *UM Effect Model*.

::: { #func.calc_user_movie_genre_effect_MSE.cv.details .sidebar }
##### Details
\

The function calculates *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: { #func.calc_user_movie_genre_effect_MSE.cv.value .sidebar }
##### Value
\

::: { #func.calc_user_movie_genre_effect_MSE.cv.code .sidebar }
##### Source Code
\

The source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is shown below:
```{r eval=FALSE}
calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
  put_log("Computing RMSEs.ResultTibble on Validation Sets...")
  start <- put_start_date()
  user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
    cv_dat$validation_set |> calc_user_movie_genre_effect_MSE(umg_effect)
  })
  put_end_date(start)

  plot(user_movie_genre_effects_MSEs)
  put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
           CVFolds_N)

  mean(user_movie_genre_effects_MSEs)
}
```

::: {.noteblock data-latex=""}
The source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) script on _GitHub_.
:::
:::

#### [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) Function {#func.calc_user_movie_genre_effect_RMSE.cv}
\

::: { #func.calc_user_movie_genre_effect_RMSE.cv.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
cv.UM_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UM_effect)

::: { #func.calc_user_movie_genre_effect_RMSE.cv.args .sidebar }
##### Arguments
\

::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect .sidebar }
  - **um_effect:** Data frame representing the *UM Effect Model*.

::: { #func.calc_user_movie_genre_effect_RMSE.cv.details .sidebar }
##### Details
\

The function calculates *Root Squared Error (RMSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].

::: { #func.calc_user_movie_genre_effect_RMSE.cv.value .sidebar }
##### Value
\

::: { #func.calc_user_movie_genre_effect_RMSE.cv.code .sidebar }
##### Source Code
\

The source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is shown below:
```{r eval=FALSE}
calc_user_movie_genre_effect_RMSE.cv <- function(um_effect){
  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
  put_log2("Function: user_movie_effects_RMSE.cv:
%1-Fold Cross-Validation ultimate RMSE: %2", length(edx_CV), um_effect_RMSE)
  um_effect_RMSE
}
```

::: {.noteblock data-latex=""}
The source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) script on _GitHub_.
:::
:::

### UMGE Model: Regularization
\

#### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) Function {#func.regularize.test_lambda.UMG_effect.cv}
\

Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument for the *User+Movie Effect (UME) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.

::: { #func.regularize.test_lambda.UMG_effect.cv.usage .sidebar }
##### Usage
\

::: { #func.regularize.test_lambda.UMG_effect.cv.args .sidebar }
##### Arguments
\

::: { #func.regularize.test_lambda.UMG_effect.cv.args.lambda .sidebar }
  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.

::: { #func.regularize.test_lambda.UMG_effect.cv.details .sidebar }
##### Details
\

The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].

::: { #func.regularize.test_lambda.UMG_effect.cv.value .sidebar }
##### Value
\

The *Root Mean Squared Errors (RMSE)* value computed for the UME Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument.

::: { #func.regularize.test_lambda.UMG_effect.cv.code .sidebar }
##### Source Code
\

The source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is shown below:
```{r eval=FALSE}
regularize.test_lambda.UMG_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.user_movie_genre_effect.cv
`lambda` is `NA`")
  }

  umg_effect <- train_user_movie_genre_effect.cv(lambda)
  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
:::
:::

### Matrix Factorization Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R) script on _GitHub_.
:::

#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) Function {#func.mf.residual.dataframe}
\

::: { #func.mf.residual.dataframe.usage .sidebar }
##### Usage
\

::: { #func.mf.residual.dataframe.args .sidebar }
##### Arguments
\

::: { #func.mf.residual.dataframe.args.file_name .sidebar }
  - **train_set:** ;

::: { #func.mf.residual.dataframe.details .sidebar }
##### Details
\

::: { #func.mf.residual.dataframe.value .sidebar }
##### Value
\

::: { #func.mf.residual.dataframe.code .sidebar }
##### Source Code
\

The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is shown below:
```{r eval=FALSE}
mf.residual.dataframe <- function(train_set){
  train_set |> 
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(rglr.UMGY_effect, by='year') |>
    left_join(rglr.UMGYD_effect, by='days') |>
    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
    select(userId, movieId, rsdl)
}
```

::: {.noteblock data-latex=""}
The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) script on _GitHub_.
:::
:::

#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
\

::: { #func.UMGYDE_model.predict.usage .sidebar }
##### Usage
\

::: { #func.UMGYDE_model.predict.args .sidebar }
##### Arguments
\

::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
  - **test_set:** ;

::: { #func.UMGYDE_model.predict.details .sidebar }
##### Details
\

::: { #func.UMGYDE_model.predict.value .sidebar }
##### Value
\

::: { #func.UMGYDE_model.predict.code .sidebar }
##### Source Code
\

The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
```{r eval=FALSE}
UMGYDE_model.predict <- function(test_set) {
  test_set |>
    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
}
```

::: {.noteblock data-latex=""}
The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
:::
:::

### 2025-11-27 reports/capstone-movielens.site/work/func-descr.template.Rmd
Report, Appendix A: UMGE Model & MF Support Functions description prototype added.

>>>>

### Matrix Factorization Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R) script on _GitHub_.
:::

#### [mf_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) Function {#func.mf_func_tmpl}
\

::: { #func.mf_func_tmpl.usage .sidebar }
##### Usage
\

::: { #func.mf_func_tmpl.args .sidebar }
##### Arguments
\

::: { #func.mf_func_tmpl.args.file_name .sidebar }
  - **file_name:** A name used as a base to generate a unique log file name;

::: { #func.mf_func_tmpl.details .sidebar }
##### Details
\

::: { #func.mf_func_tmpl.value .sidebar }
##### Value
\

::: { #func.mf_func_tmpl.code .sidebar }
##### Source Code
\

The source code of the [mf_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the [mf_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) script on _GitHub_.
:::
:::
